% Part: Sets, Relations, Functions
% From projeto: THE OPEN LOGIC TEXT
% 01/06/2020 - LUIS HENRIQUE BUSTAMANTE

\documentclass[../../include/open-logic-part]{subfiles}

\begin{document}

\part{Sets, Relations, Functions}
\olpart{sfr}{Sets, Relations, Functions}

\begin{editorial}
  The material in this part is a reasonably complete introduction to basic naive set theory. Unless students can be assumed to have this background, it's probably advisable to start a course with a review of this material, at least the part on sets, functions, and relations. This should ensure that all students have the basic facility with mathematical notation required for any of the other logical sections. NB: This part does not cover induction directly.The presentation here would benefit from additional examples, especially, ``real life'' examples of relations of interest to the audience. It is planned to expand this part to cover naive set theory more extensively.
\end{editorial}


\begin{editorial}
  This file includes the first four chapters of the part on Na\"ive
  Set Theory, in the original slowpaced version. The complete part is
  included by \verb|sets-functions-relations-complete.tex|. The
  material in this part is a reasonably complete introduction to basic
  naive set theory. Unless students can be assumed to have this
  background, it's probably advisable to start a course with a review
  of this material, at least the part on sets, functions, and
  relations. This should ensure that all students have the basic
  facility with mathematical notation required for any of the other
  logical sections.
\end{editorial}

\olimport[sets]{sets}

\olimport[relations]{relations}

\olimport[functions]{functions}

%\olimport[size-of-sets]{size-of-sets}

\OLEndPartHook
\end{document}
